Extreme Value Chapter

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Working on Figure 1

```{r libraries}
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
```

@@

@@

# TEST VALUES --------------------------------------
## Thresholds ----------------
# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
# But we can know the quantiles of our sample.
# summary(truth_df$x_samps)
# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))

thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
tibble(thresh_tests) %>%
  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
         theta = n_overthresh/tru_n) -> thetas
thetas

@@

# Figure 2
Show the first comparisson between the Lomax and Lomax GLM estimations

```{r}
nreps_mles_df %>% 
  ggplot()

@@

>>>>

```{r libraries}
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(MetBrewer)
```

@@

```{r}
# Color palettes

pal_sampsize <- met.brewer("Hokusai3", n = 6)
pal_threshold <- met.brewer("Derain", n = 7)
pal_mixture <- met.brewer("Hokusai1", n = 4)
theta_color <- "steelblue"

@@

# TEST VALUES --------------------------------------
## Thresholds ----------------
# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
# But we can know the quantiles of our sample.
# summary(truth_df$x_samps)
# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
tru_n <- 50000
w_samp_sizes <- pis*tru_n

thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
tibble(thresh_tests) %>%
  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
         theta = n_overthresh/tru_n) -> thetas

@@

The actual values of theta for the 50k sample we took from the mixture distribution:

```{r}
thetas %>% 
  knitr::kable()
```

# Figure 2
First let's see the true thetas, which because of small numbers we are visualizing in log scale for the second panel:

```{r fig.width=10, fig.height=3}
thetas %>% 
  ggplot(., aes(x = thresh_tests, y = theta)) +
  geom_point(size = 4, shape = 18, color = theta_color) +
  labs(x = "Long-distance level", y = "Theta") +
  theme_bw() -> a

thetas %>% 
  ggplot(., aes(x = thresh_tests, y = theta)) +
  geom_point(size = 4, shape = 18, color = theta_color) +
  labs(x = "Long-distance level", y = "Theta", Title = "Log Scale") +
  theme_bw() +
  scale_y_log10() -> b

plot_grid(a, b, ncol = 2)

@@

Now, we explore how the estimates compare. These are already in log scale because they are small:

```{r fig.width=12}
nreps_mles_df %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_point() +
  labs(x = "Long-distance level", y = "Estimated thetas") +
  theme_bw()
